\documentclass[a4paper,12pt]{report}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst,setspace,subcaption}
\usepackage{amsmath,amssymb,graphicx,xcolor,url}
\usepackage{fancyhdr,tocbasic,titlesec,listings}
\usepackage[a4paper,margin=24mm]{geometry}
\usepackage[skip=10pt plus1pt, indent=20pt]{parskip}
\usepackage[colorlinks=true,allcolors=blue,urlcolor=magenta]{hyperref}

\renewcommand{\thesection}{\arabic{section}}

% Header and footer styling
\pagestyle{fancy}
\setlength{\headheight}{15pt}
\fancyhf{}
\fancyhead[R]{\nouppercase\rightmark\hfill~Lab report}
\fancyfoot[C]{\hfill\thepage\hfill}

% TOC styling
\DeclareTOCStyleEntry[
  indent=12pt,
  level=1
]{largetocline}{section}

% Title page data
\title{Implementing Hash Table from scratch}
\author{Ngo Nguyen The Khoa -- 23127065 -- 23CLC09}
\date{August 6, 2024}

\begin{document}

% Title page and TOC
\input{title_page}
\tableofcontents\thispagestyle{empty}

\pagebreak
\input{texs/HowIImplemented.tex}

\pagebreak
\section{Result Screenshots}
\input{texs/Linear Probing/result.tex}
\input{texs/Quadratic Probing/result.tex}
\input{texs/Chaining AVL/result.tex}
\input{texs/Chaining Linked List/result.tex}
\input{texs/Double Hashing/result.tex}

\pagebreak
\section{Experiments}
\input{texs/Linear Probing/experiment.tex}
\input{texs/Quadratic Probing/experiment.tex}
\input{texs/Chaining AVL/experiment.tex}
\input{texs/Chaining Linked List/experiment.tex}
\input{texs/Double Hashing/experiment.tex}

\pagebreak
\section{Self-evaluation}
\begin{center}
  \renewcommand{\arraystretch}{1.5}
  \begin{tabular}{|l|p{\dimexpr0.6\linewidth-2\tabcolsep}|c|}
    \hline
    \textbf{No.} & \textbf{Details}           & \textbf{Score} \\ \hline
    1            & Linear Probing             & 100\%          \\ \hline
    2            & Quadratic Probing          & 100\%          \\ \hline
    3            & Chaining using Linked List & 100\%          \\ \hline
    4            & Chaining using AVL Tree    & 100\%          \\ \hline
    5            & Double Hashing             & 100\%          \\ \hline
    6            & Experiments                & 100\%          \\ \hline
    7            & Report                     & 100\%          \\ \hline
  \end{tabular}
\end{center}

\pagebreak
\section{Exercise Feedback}
\subsection{What I have learned from this Exercise}
\begin{flushleft}
  Because almost the things could be done easily, I have learned a few things new from this exercise.
  \begin{itemize}
    \item I have learned how to implement the hash table using different methods of collision handling.
    \item I have learned how to use rehashing to solve the collisions.
    \item I also know how to test the hash table using different test cases.
    \item Have a strong understanding of the hash table and its methods is the big thing I got after finishing this Exercise.
  \end{itemize}
\end{flushleft}
\subsection{What I found challenging}
\begin{flushleft}
  This exercise is quite simple and easy, so I have no difficulties to finish this task.
\end{flushleft}
\subsection{What I have used in this exercise}
\begin{itemize}
  \item I used C++ to implement the data structures and the test cases.
  \item I also used \LaTeX{} to write this report.
\end{itemize}
\end{document}